---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# maldipickrGUI

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `{maldipickrGUI}` is to provide an interactive interface to run reproducible workflow to dereplicate and cherry-pick mass spectrometry spectra using the [`{maldipickr}`](https://cran.r-project.org/package=maldipickr), in order to reduce the redundancy of bacterial isolates.

The interface is a [`{shiny}`](https://cran.r-project.org/package=shiny) application, built using the robust [`{golem}`](https://cran.r-project.org/package=golem) framework.
Reproducible workflows are created using [`{targets}`](https://docs.ropensci.org/targets/).


## Installation

You can install the development version of `{maldipickrGUI}` using
the following command in R:

```{r install_github, eval = FALSE}
remotes::install_github("ClavelLab/maldipickrGUI")
```

## Code of Conduct

Please note that the `{maldipickrGUI}` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

